---
title: "Tutorial 2"
author: "Wang Zhe"
date: "Febrary 3, 2016"
output: md_document
---

```{r, message=FALSE, echo=FALSE}
setwd('/Users/wang/Desktop')
data = read.csv('labs.csv')

library(ggplot2)
library(dplyr)
library(plyr)
```

1a i)
```{r, message=FALSE, echo=FALSE}
paste("Statistical Index: ", mean(data$WaitTime))
barplot(data$WaitTime)
abline(h=mean(data$WaitTime))
```
The KPI of Waiting time is 69.77

1a ii)
```{r, message=FALSE, echo=FALSE}
mytable <- table(data$SvcSat)
piepercent<- round(100*mytable/sum(mytable), 1)
mytable <-piepercent
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, main="Pie Chart of Service Satisfaction\n (with sample sizes %)")
```
The KPI of Service Satisfaction is 83.4%

1b
```{r, message=FALSE, echo=FALSE}
data$newSat[data$SvcSat=='Y']=1
data$newSat[data$SvcSat=='N']=0
data$newGen[data$Gender=='M']=1
data$newGen[data$Gender=='F']=0

ggplot(data, aes(data$AGE,data$newSat)) + geom_point()+geom_smooth()

summary(lm(data$newSat ~ data$AGE + data$newGen))
```
As we can see the p-value is small, there is negative coefficient between Service Satisfation and AGE.
The slope is negative for Age, it shows us that younger people has higher service satisfaction.
The slope is negative for Gender, it shows us that female has higher service satisfaction than male.

1c
```{r, message=FALSE, echo=FALSE}
cor.test(data$newSat,data$WaitTime)
ggplot(data, aes(data$newSat, data$WaitTime)) + geom_line()
```
It has a -0.53, a strong negative correlation between wait time and service satisfaction.
It shows that shorter wait time has higher service satisfaction.

1d
```{r, message=FALSE, echo=FALSE}
data <- mutate(data, BMI = WT/(HT*HT))
cor.test(data$BMI, as.integer(data$TC))
plot(data$BMI, as.integer(data$TC), main="Scatterplot", xlab="BMI", ylab="Total Cholesterol", pch=19)
```
It has a 0.48, a medium positive correlation between bmi and total cholesterol.
A higher BMI may lead to High Total Cholesterol.

1e
```{r, message=FALSE, echo=FALSE}
fit <- lm(BMI~AGE+SBP+as.integer(TC), data = data)
predict(fit, newdata = data.frame(AGE=45, SBP=135, TC=150))
```
The predicted BMI is 29.78
The assumption is that there is correlation between BMI and age, systolic blood pressure, total cholesterol.
But this does not imply there is casuation.

